A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-05-04 report_clean/absorption.tex
fixed typos
fixed small typos

We normalize  $\epsilon_0=\mu_0=1$ and $\omega=c=1$. 
Also, we set $m_e=1$ and $e=-1$. From this it follows that $w_c=-B_0$ and $w_p^2=N_e$. 
We consider the following two cases:
\begin{itemize}
 \item case $N_e\neq \operatorname{const}$, no resonance;
 \item case $N_e\neq \operatorname{const}$, resonance.
\end{itemize}
For every fixed absorption rate \urev{$\nu>0$}, in the time domain we choose the boundary conditions of the form
\begin{align}
\label{eq:bcs}
\left.\partial_t H\right|_{x=-L}&=-\left.\partial_x E_y\right|_{x=-L}=G\sin(t),\; G\in \mathbb{R}, \\
 \nonumber
 \left.\partial_t H\right|_{x=H}&=0,
\end{align}
and zero initial conditions, and in the frequency domain
\bealn
 \left.\partial_x \hat{E}_y\right|_{x=-L}=G,\; \left.\partial_x \hat{E}_y\right|_{x=H}=0.
\eealn
We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain 
(the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain. 
In the numerical experiments we check whether the following two quantities
\ben
\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\exp(\mrev{-it})\right)
\een
are close as $\nu\rightarrow 0$ (provided that the first of these quantities exists).

In all the experiments in this section the CFL number was chosen as 0.5.
\subsubsection{No-Resonance Case}
\label{section:absorption_airy}
We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{y}^{\nu},\; \nu=0,$ satisfies 
the Airy equation, c.f. also Remark \ref{remark:other}. We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
choose the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x>0,\; x\in \Omega$. 
\urev{Importantly, since $\delta(x)=0$, in this case no resonance occurs and $\hat{E}_x(x)\equiv 0$. This corresponds to the case when the
tensor of dielectric permittivity $\uuline{\varepsilon^{\nu}_{\omega}}$ is 
diagonal.}

@@

First we set $\nu=10^{-2}$. To demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
inside the domain and plot the dependence of the solution $E_{y}^{\nu}(x_c,t), \; \Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{\mrev{-it}}\right)$ 
on time $t$ for a range of $t\gg 1$ in Fig.~\ref{fig:nu1e2_harmon}. We compare this solution to the computed $\Im\left(\hat{E}_y^{\nu}\mathrm{e}^{\mrev{-it}}\right)$, for
fixed values of $t$. Both solutions appear to be in close agreement.

@@

\FloatBarrier
Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=1e-4$. As previously, 
 we fix a point $x=x_c$ inside the domain and plot 
the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$ for a range of $t\gg 1$. 
One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution. 
For $\nu=10^{-4}$ we were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$. 
For example, for $\nu=10^{-6}$ we were not able to reach the limiting amplitude solution even on the time interval $t\leq 1.92e6$, 
see Fig.~\ref{fig:nu1e4_harmon} (right). 
\begin{figure}
\begin{tabular}{cc}
 \includegraphics[width=0.45\textwidth]{pics_time_domain/airy/figure_nu1e4-crop.pdf}&
 \includegraphics[width=0.45\textwidth]{pics_time_domain/airy/figure_nu1e6-crop.pdf}\\
\end{tabular}
\caption{In the left figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ \urev{to the problem described in Section \ref{section:absorption_airy}} on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$. 
In the right figure we show the solution \urev{to the same problem} for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
$\nu=10^{-4}$ the limiting amplitude solution was reached for large $t$. For $\nu=10^{-6}$ we were not able 
to obtain the limiting amplitude solution even for $t\approx 1.9e6$. }
  \label{fig:nu1e4_harmon}
\end{figure}

>>>>

We normalize  $\epsilon_0=\mu_0=1$ and $\omega=c=1$. 
Also, we set $m_e=1$ and $e=-1$. From this it follows that $w_c=-B_0$ and $w_p^2=N_e$. 
We consider the following two cases:
\begin{itemize}
 \item case $N_e\neq \operatorname{const}$, no resonance;
 \item case $N_e\neq \operatorname{const}$, resonance.
\end{itemize}
For every fixed absorption rate \urev{$\nu>0$}, in the time domain we choose the boundary conditions of the form
\begin{align}
\label{eq:bcs}
\left.\partial_t H\right|_{x=-L}&=-\left.\partial_x E_y\right|_{x=-L}=G\sin(t),\; G\in \mathbb{R}, \\
 \nonumber
 \left.\partial_t H\right|_{x=H}&=0,
\end{align}
and zero initial conditions, and in the frequency domain
\bealn
 \left.\partial_x \hat{E}_y\right|_{x=-L}=G,\; \left.\partial_x \hat{E}_y\right|_{x=H}=0.
\eealn
We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain, and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain. 
In the numerical experiments we check whether the following two quantities
\ben
\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\exp(\mrev{-it})\right)
\een
are close as $\nu\rightarrow 0$ (provided that the first of these quantities exists).

In all the experiments in this section the CFL number was chosen as 0.5.
\subsubsection{No-Resonance Case}
\label{section:absorption_airy}
We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{y}^{\nu},\; \nu=0,$ satisfies 
the Airy equation, c.f. also Remark \ref{remark:other}. We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
choose the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x>0,\; x\in \Omega$. 
\urev{Importantly, since $\delta(x)=0$, in this case no resonance occurs and $E(x,t)\equiv 0$. This corresponds to the case when the
tensor of dielectric permittivity $\uuline{\varepsilon^{\nu}_{\omega}}$ is 
diagonal.}

@@

First we set $\nu=10^{-2}$. To demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
inside the domain and plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ 
on time $t$ for a range of $t\gg 1$ in Fig.~\ref{fig:nu1e2_harmon}. We compare this solution to the computed $\Im\left(\hat{E}_y^{\nu}\mathrm{e}^{\mrev{-it}}\right)$, for
fixed values of $t$. Both solutions appear to be in close agreement.

@@

\FloatBarrier
Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=10^{-4}$. As previously, 
 we fix a point $x=x_c$ inside the domain and plot 
the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$ for a range of $t\gg 1$. 
One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution. 
For $\nu=10^{-4}$ we were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$. 
For example, for $\nu=10^{-6}$ we were not able to reach the limiting amplitude solution even on the time interval $t\leq 1.92e6$, 
see Fig.~\ref{fig:nu1e4_harmon} (right). 
\begin{figure}
\begin{tabular}{cc}
 \includegraphics[width=0.45\textwidth]{pics_time_domain/airy/figure_nu1e4-crop.pdf}&
 \includegraphics[width=0.45\textwidth]{pics_time_domain/airy/figure_nu1e6-crop.pdf}\\
\end{tabular}
\caption{In the left figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ \urev{to the problem described in Section \ref{section:absorption_airy}} on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$. 
In the right figure we show the solution \urev{to the same problem} for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
$\nu=10^{-4}$ the limiting amplitude solution was reached for large $t$. For $\nu=10^{-6}$ we were not able 
to obtain the limiting amplitude solution even for $t\approx 1.9e6$. }
  \label{fig:nu1e4_harmon}
\end{figure}

### 2015-05-04 report_clean/intro.tex
intro.tex modified
fixed typos
fixed small typos

The energy of this system in a domain $\Omega\in\mathbb R^2$ can be expressed as, see \cite{Despres_2014},
\ben
{\mathcal E}(t)= \int_\Omega \left(
\frac{\epsilon_0 |\E(t,\mathbf{r})|^2}{2}+\frac{ |\B(t,\mathbf{r})|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|^2}{2|e|N_e(\mathbf{r})} 
\right)\mathrm{d}\mathbf{r},
\een
and
\ben
\frac{d}{dt}{\mathcal E}=-\nu\left(\|u_{x}\|_{L_{2}(\Omega)}^2+\|u_{y}\|_{L_{2}(\Omega)}^2\right)+\text{boundary terms}.
\een

@@

As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
integrable. This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.

@@

In this article we concentrate on a simplified model (which nevertheless is of physical interest when modelling antennas in plasmas), 
where it is required to study the above system under the assumption that the electron density $N_{e}$ and the magnetic field $B_0$ are \textbf{uniform} in the second coordinate, more precisely 
$N_{e}=N_{e}(x)$ and $B_0=B_0(x)$, see e.g. \cite{Despres_2014}. Even this simplified case contains difficulties intrinsic to hybrid resonance \cite{Despres_2014, singular_solutions}.

Under the aforementioned assumptions on $N_e$ and $B_0$, the one-dimensional model can be derived from (\ref{eq:main_system}) by performing the Fourier transform in $y$ ($\partial_y\rightarrow i\theta, \; \theta\in\mathbb{R}$). For a parameter $\theta$,
\begin{equation}
 \label{eq:main_model}
\begin{cases}
\epsilon_0\partial_t E_{x}-i\theta H_z=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\\
\mu_0\partial_t H_z+\partial_x E_y-i\theta E_x =0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
\end{cases}
\end{equation}
 posed in $(-L,\; H)$, for some $L,H>0$, with \mrev{the boundary conditions as in (\ref{eq:boundary_conditions_intro}),
 \begin{align}
 \label{eq:boundary_conditions_frequency_domain}
 \begin{split}
  \left.\left(\partial_x E_y -i\theta E_x-i\lambda E_y\right)\right|_{x=-L} =g_{inc}(t),\\
  \left.\partial_xE_y\right|_{x=H}=0, 
  \end{split}
 \end{align}
and the initial conditions for values $\left.E_{x}\right|_{t=0},\; \left.u_{x}\right|_{t=0},\; \left.E_{y}\right|_{t=0}, \; \left.u_{y}\right|_{t=0}, \; \left.H_z\right|_{t=0}$. }

@@

In the frequency domain (\ref{eq:main_model}) for $\nu=0$ is of the form 
\begin{align}
\label{eq:main_frequency_domain_intro}
\left(
\begin{matrix}
 i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
 i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\uuline{\varepsilon_{\omega}^{0}}(x)\left(
\begin{matrix}
 \hat{E}_x\\
 \hat{E}_y
\end{matrix}
\right)
=0,
\end{align}
see (\ref{eq:alpha_delta}). Indeed, the coefficients $\alpha_{\omega},\;\delta_{\omega}$ depend solely on $x$ and $\omega$.  
\arev{
We concentrate on a physical situation of the hybrid resonance, which we define as in \cite{singular_solutions}.
\begin{df}
Let $\omega\in\mathbb{R}$ be fixed. 
We will call a point $x_h\in \mathbb{R}$ a hybrid resonance if $\alpha_{\omega}$ has 
a simple root in $x_h$ and has no other roots in an $\epsilon$-vicinity of this point $B_{\epsilon}(x_h)$, for some $\epsilon>0$, and 
$\delta(x_h)\neq 0$. 
\end{df}
}

To investigate the behaviour of the solutions in the case when the hybrid resonance occurs in the sustem, 
instead of the above problem we will study a sequence of the regularized problems, for $\nu\rightarrow 0$, 
\begin{align}
\label{eq:seq_regularized}
\left(
\begin{matrix}
 i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
 i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\left(\uuline{\varepsilon_{\omega}^{0}}(x)+i\nu \mathrm{Id}\right)\left(
\begin{matrix}
 \hat{E}_x\\
 \hat{E}_y
\end{matrix}
\right)
=0,
\end{align}
where $\mathrm{Id}$ is the identity matrix. More details on the connection of this problem with (\ref{eq:main_model}) will be provided in further sections.

@@

The goal of this article is three-fold. 
First, we investigate the finite element approximation of the 1D 
problem (\ref{eq:seq_regularized}), with a dielectric tensor \mrev{regularized
with the help of a small parameter $\nu$}. 
%linearized with respect to $\nu$.
We prove the well-posedness of this problem for \mrev{$\nu\neq 0$} in Section~\ref{sec:wellposedness} and 
demonstrate that the use of  (P1) finite elements allows to approximate the singularity 
of the solution fairly well (Section \ref{sec:freq_dep}). 
}

Second, we briefly develop an original scheme based on widely appreciated semi-lagrangian schemes
for the discretization of time domain Maxwell's equations with a linear current.
Thirdly, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
the FDTD discretization of \eqref{eq:main_model}, suggested in \cite{stable_yee_plasma_current}. 
We compare this result with 
$\hat{\mathbf{E}}\mathrm{e}^{\mrev{-i\omega} t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
\urev{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
In application to a non-resonant case of (\ref{eq:main_frequency_domain_intro}), equipped with boundary conditions, the limited absorption principle states that the solution of (\ref{eq:seq_regularized}) would coincide with the solution of (\ref{eq:main_frequency_domain_intro})
as $\nu\rightarrow 0$. Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_model}) 
states that if the boundary conditions are chosen harmonic in time, e.g. $\left.\partial_x E_y\right|_{x=-L}=\mathrm{e}^{-i\omega_{*} t}$, then the solution of this problem $(\mathbf{E}(t),\;H(t))$ asymptotically ($t\rightarrow +\infty$)
tends to a steady state of the form $ \left(\mathbf{E}(\omega_{*}),\; \hat{H}(\omega_{*})\right)\mathrm{e}^{-i\omega_{*} t}$, where 
$\left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)$ is the solution of (\ref{eq:main_model})
in the frequency domain, with $\omega=\omega_{*}$ and the boundary condition $\left.\partial_x \hat{E}_y\right|_{x=-L}=1$. For more details see e.g. \cite{Morawetz, Eidus}. The commutation between the two principles then write as}
$$
\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0},
$$
see Figure \ref{fig:limits}. 
Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in our case due to the singularity
of the hybrid resonance.
\begin{figure}
\begin{tikzpicture}
   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
    \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
     };
 \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow+\infty$} (m-2-1);
  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
 \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow +\infty$} (m-2-2);

>>>>

The energy of this system in a domain $\Omega\in\mathbb R^2$ can be expressed as, see \cite{Despres_2014},
\ben
{\mathcal E}(t)= \int_\Omega \left(
\frac{\epsilon_0 |\E(t,\mathbf{r})|^2}{2}+\frac{ |\B(t,\mathbf{r})|^2}{2\mu_0}+\frac{m_e|\J (t,\mathbf{r})|^2}{2|e|N_e(\mathbf{r})} 
\right)\mathrm{d}\mathbf{r},
\een
and
\ben
\frac{d}{dt}{\mathcal E}=-\nu\left(\|u_{x}\|_{L^{2}(\Omega)}^2+\|u_{y}\|_{L^{2}(\Omega)}^2\right)+\text{boundary terms}.
\een

@@

As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
integrable (for a demonstration of this behaviour with the help of a simpler example, namely the Whittaker problem, see e.g. \cite{Despres_2014}). 
This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.

@@

In this article we concentrate on a simplified model (which nevertheless is of physical interest when modelling antennas in plasmas), 
where it is required to study the above system under the assumption that the electron density $N_{e}$ and the magnetic field $B_0$ are \textbf{uniform} in the second coordinate, more precisely 
$N_{e}=N_{e}(x)$ and $B_0=B_0(x)$, see e.g. \cite{Despres_2014}. 
We additionally assume that $N_e>0$ on $[-L,\;H]$. Even this simplified case contains difficulties intrinsic to the hybrid resonance \cite{Despres_2014, singular_solutions}.

Under the aforementioned assumptions on $N_e$ and $B_0$, the one-dimensional model can be derived from (\ref{eq:main_system}) by performing the Fourier transform in $y$ ($\partial_y\rightarrow i\theta, \; \theta\in\mathbb{R}$):
\begin{equation}
 \label{eq:main_model}
\begin{cases}
\epsilon_0\partial_t E_{x}-i\theta H_z=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\\
\mu_0\partial_t H_z+\partial_x E_y-i\theta E_x =0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y,
\end{cases}
\end{equation}
 posed in $(-L,\; H)$, for some $L,H>0$, with \mrev{the boundary conditions as in (\ref{eq:boundary_conditions_intro})
 \begin{align}
 \label{eq:boundary_conditions_frequency_domain}
 \begin{split}
  \left.\left(\partial_x E_y -i\theta E_x+i\lambda E_y\right)\right|_{x=-L} =g_{inc}(t),\\
  \left.\partial_xE_y\right|_{x=H}=0, 
  \end{split}
 \end{align}
and the initial conditions for values $\left.E_{x}\right|_{t=0},\; \left.u_{x}\right|_{t=0},\; \left.E_{y}\right|_{t=0}, \; \left.u_{y}\right|_{t=0}, \; \left.H_z\right|_{t=0}$. }

@@

In the frequency domain (\ref{eq:main_model}) for $\nu=0$ is of the form 
\begin{align}
\label{eq:main_frequency_domain_intro}
\left(
\begin{matrix}
 i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
 i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\uuline{\varepsilon_{\omega}^{0}}(x)\left(
\begin{matrix}
 \hat{E}_x\\
 \hat{E}_y
\end{matrix}
\right)
=0,
\end{align}
see (\ref{eq:alpha_delta}). Indeed, the coefficients $\alpha_{\omega},\;\delta_{\omega}$, see (\ref{eq:alpha_delta}), in this case depend solely on $x$ and $\omega$.  
\arev{
We concentrate on a physical situation of the hybrid resonance, which we define as in \cite{singular_solutions}.
\begin{df}
Let $\omega\in\mathbb{R}$ be fixed. 
We will call a point $x_h\in \mathbb{R}$ a hybrid resonance if $\alpha_{\omega}$ has 
a simple root in $x_h$ and has no other roots in an $\epsilon$-vicinity of this point $B_{\epsilon}(x_h)$, for some $\epsilon>0$, 
and $\delta_{\omega}(x_h)\neq 0$.
\end{df}
}

To investigate the behaviour of the solutions in the case when the hybrid resonance occurs in the system, 
instead of the above problem we will study a sequence of the regularized problems, for $\nu\rightarrow 0$, 
\begin{align}
\label{eq:seq_regularized}
\left(
\begin{matrix}
 i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
 i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\left(\uuline{\varepsilon_{\omega}^{0}}(x)+i\nu \mathrm{Id}\right)\left(
\begin{matrix}
 \hat{E}_x\\
 \hat{E}_y
\end{matrix}
\right)
=0,
\end{align}
where $\mathrm{Id}$ is the identity matrix. More details on the connection of this problem with (\ref{eq:main_model}) will be provided in further sections.

@@

The goal of this article is three-fold. 
First, we investigate the finite element approximation of the 1D 
problem (\ref{eq:seq_regularized}), with a dielectric tensor \mrev{regularized
with the help of a small parameter $\nu$}. 
%linearized with respect to $\nu$.
We prove the well-posedness of this problem for \mrev{$\nu\neq 0$} in Section~\ref{sec:wellposedness} and 
demonstrate that the use of  $P_1$ finite elements allows to approximate the singularity 
of the solution fairly well (Section \ref{sec:freq_dep}). 
}

Second, we briefly develop an original scheme based on widely appreciated semi-lagrangian schemes
for the discretization of time domain Maxwell's equations with a linear current.
Thirdly, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
the FDTD discretization of \eqref{eq:main_model}, suggested in \cite{stable_yee_plasma_current}. 
We compare this result with 
$\hat{\mathbf{E}}\mathrm{e}^{\mrev{-i\omega} t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
\urev{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
In application to a non-resonant case of (\ref{eq:main_frequency_domain_intro}), equipped with boundary conditions, the limited absorption principle states that the solution of (\ref{eq:seq_regularized}) 
would approach the solution of (\ref{eq:main_frequency_domain_intro})
as $\nu\rightarrow 0$. Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_model}) 
states that if the boundary conditions are chosen harmonic in time, e.g. $\left.\partial_x E_y\right|_{x=-L}=\mathrm{e}^{-i\omega_{*} t}$, then the solution of this problem $(\mathbf{E}(t),\;H(t))$ asymptotically ($t\rightarrow +\infty$)
tends to a steady state of the form $ \left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)\mathrm{e}^{-i\omega_{*} t}$, where 
$\left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)$ is the solution of (\ref{eq:main_model})
in the frequency domain, with $\omega=\omega_{*}$ and the boundary condition $\left.\partial_x \hat{E}_y\right|_{x=-L}=1$. For more details see e.g. \cite{Morawetz, Eidus}. The commutation between the two principles then writes as}
$$
\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0},
$$
see Figure \ref{fig:limits}. 
Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in our case due to the singularity
of the hybrid resonance.
\begin{figure}
\begin{tikzpicture}
   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
    \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
     };
 \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow+\infty$} (m-2-1);
  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
 \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow +\infty$} (m-2-2);
